---
title: "demographics"
author: "SL"
date: "5/23/2021"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(haven)
library(Hmisc)
library(janitor)
library(skimr)
library(zoo)
library(naniar)
library(readxl)
library(simstudy)

```



Import demographics from DMED queries

```{r}

setwd("C:/Users/slewa/OneDrive - cumc.columbia.edu/risk_factors")

demog <-
  readxl::read_xlsx(path = "./data/dmed_demog.xlsx", sheet = "all",
                    col_names = TRUE) %>% 
  mutate(year = as.factor(year))

```


Wrangle from wide to long



```{r}

# proportion for each variable-category/year
# population sum for each category-year



demog_long <-
  demog %>% 
    pivot_longer(-year, names_to = "var", values_to = "population") %>% 
      mutate(var = as.factor(var),
             cat = as.factor(str_replace_all(var, "[:digit:]", ""))) %>% 
  nest(data = c(var, population)) %>% 
  mutate(data = 
           map(.x = .$data, ~ .x %>% 
                      mutate(proportion = population / sum(population),
                             sum_pop = sum(population)))) %>% 
  unnest(cols = c(data))
  


# Note: population sums vary slightly between categories in a given year
  # race and service match with the highest counts (use service population total)

demog_long %>% 
  group_by(year, cat) %>% 
  summarise(sum_pop = mean(sum_pop)) %>% View()

```




## Simulate active duty population for each year


```{r}


demographics <- 
  demog_long %>%
    nest(data = -year) %>% 
    mutate(pop = map(data, ~ (.) %>% filter(var %in% "service1") %>% pull(sum_pop) %>% round(., digits = 0))) %>% 
  unnest(pop)

# Note: total population based on "service" used for all categories each year



set.seed(82)

sim_fun = function(df, pop) {
    data.frame(
      age = sample(x= 1:6, size = pop, replace = TRUE, prob = c(
        df %>% filter(var %in% "age1") %>% pull(proportion),
        df %>% filter(var %in% "age2") %>% pull(proportion),
        df %>% filter(var %in% "age3") %>% pull(proportion),
        df %>% filter(var %in% "age4") %>% pull(proportion),
        df %>% filter(var %in% "age5") %>% pull(proportion),
        df %>% filter(var %in% "age6") %>% pull(proportion)
        )),
      sex = sample(x = 1:2, size = pop, replace = TRUE, prob = c(
        df %>% filter(var %in% "sex1") %>% pull(proportion),
        df %>% filter(var %in% "sex2") %>% pull(proportion)
         )),
      grade = sample(x = 1:4, size = pop, replace = TRUE, prob = c(
        df %>% filter(var %in% "grade1") %>% pull(proportion),
        df %>% filter(var %in% "grade2") %>% pull(proportion),
        df %>% filter(var %in% "grade3") %>% pull(proportion),
        df %>% filter(var %in% "grade4") %>% pull(proportion)
      )),  
      race = sample(x = 1:3, size = pop, replace = TRUE,prob = c(
        df %>% filter(var %in% "race1") %>% pull(proportion),
        df %>% filter(var %in% "race2") %>% pull(proportion),
        df %>% filter(var %in% "race3") %>% pull(proportion)
      )),  
      service = sample(x = 1:4, size = pop, replace = TRUE, prob = c(
        df %>% filter(var %in% "service1") %>% pull(proportion),
        df %>% filter(var %in% "service2") %>% pull(proportion),
        df %>% filter(var %in% "service3") %>% pull(proportion),
        df %>% filter(var %in% "service4") %>% pull(proportion)
    ))
  )
}



sim_df <-
  map2(.x = demographics$data, .y = demographics$pop, .f = sim_fun)




```










--------------------------------------------------------------------------
Draft code 

```{r}


  data.frame(
    age = sample(x= 1:6, size = 10000, replace = TRUE, prob = c(
      . %>% filter(var %in% "age1") %>% pull(proportion),
      . %>% filter(var %in% "age2") %>% pull(proportion),
      . %>% filter(var %in% "age3") %>% pull(proportion),
      . %>% filter(var %in% "age4") %>% pull(proportion),
      . %>% filter(var %in% "age5") %>% pull(proportion),
      . %>% filter(var %in% "age6") %>% pull(proportion)
      )),
    sex = sample(x = 1:2, size = 10000, replace = TRUE, prob = c(
      . %>% filter(var %in% "sex1") %>% pull(proportion),
      . %>% filter(var %in% "sex2") %>% pull(proportion)
       )),
    grade = sample(x = 1:4, size = 10000, replace = TRUE, prob = c(
      . %>% filter(var %in% "grade1") %>% pull(proportion),
      . %>% filter(var %in% "grade2") %>% pull(proportion),
      . %>% filter(var %in% "grade3") %>% pull(proportion),
      . %>% filter(var %in% "grade4") %>% pull(proportion)
    )),  
    race = sample(x = 1:3, size = 10000, replace = TRUE,prob = c(
      . %>% filter(var %in% "race1") %>% pull(proportion),
      . %>% filter(var %in% "race2") %>% pull(proportion),
      . %>% filter(var %in% "race3") %>% pull(proportion)
    )),  
    service = sample(x = 1:4, size = 10000, replace = TRUE, prob = c(
      . %>% filter(var %in% "service1") %>% pull(proportion),
      . %>% filter(var %in% "service2") %>% pull(proportion),
      . %>% filter(var %in% "service3") %>% pull(proportion),
      . %>% filter(var %in% "service4") %>% pull(proportion)
    ))
)



data_1990 <-
  demog_long %>%
    filter(year %in% "1990") %>% 
    dplyr::select(-year)





data.frame(
  age = sample(1:6, pop, replace = TRUE, prob = c(p1a, p2a, p3a, p4a, p5a, p6a)),
  sex = sample(1:2, pop, replace = TRUE, prob = c(p1s, p2s)),
  grade = sample(1:4, pop, replace = TRUE, prob = c(p1g, p2g, p3g, p4g)),  
  race = sample(1:3, pop, replace = TRUE, prob = c(p1r, p2r, p3r)),  
  service = sample(1:4, pop, replace = TRUE, prob = c(p1ser, p2ser, p3ser, p4ser))
)
  
  data_1990 %>% 
  

  
sample(c('male', 'female'), 10000, replace=TRUE)

 sample( LETTERS[1:4], 10000, replace=TRUE, prob=c(0.1, 0.2, 0.65, 0.05) ) %>% 
   as_tibble()
```







## Simstudy code
`simstudy` package

categorical
A categorical distribution is a discrete data distribution taking on values from 1 to K, with each value representing a specific category, and there are K categories. The categories may or may not be ordered. For a categorical variable with k categories, the formula is a string of probabilities that sum to 1, each separated by a semi-colon: (p1;p2;...;pk). p1 is the probability of the random variable falling in category 1, p2 is the probability of category 2, etc. The probabilities can be specified as functions of other variables previously defined. The link options are identity or logit. The variance field does not apply to the categorical distribution.

```{r}

set.seed(82)



def <- simstudy::defData(varname = "age", dist = "categorical", 
                         formula = "p1a;p2a;p3a;p4a;p5a;p6a")

def <- simstudy::defData(def, varname = "sex", dist = "categorical", 
                         formula = "p1s;p2s")

def <- simstudy::defData(def, varname = "grade", dist = "categorical", 
                         formula = "p1g;p2g;p3g;p4g")

def <- simstudy::defData(def, varname = "race", dist = "categorical", 
                         formula = "p1r;p2r;p3r")

def <- simstudy::defData(def, varname = "service", dist = "categorical", 
                         formula = "p1ser;p2ser;p3ser;p4ser")

def




sample_df <-
  demog_long %>% filter(year %in% "2019")



def <- simstudy::defData(varname = "age", dist = "categorical", 
                         formula = genCatFormula(p1a,p2a,p3a,p4a,p5a,p6a))

def <- simstudy::defData(def, varname = "sex", dist = "categorical", 
                         formula = genCatFormula(p1s,p2s))

def <- simstudy::defData(def, varname = "grade", dist = "categorical", 
                         formula = genCatFormula(p1g,p2g,p3g,p4g))

def <- simstudy::defData(def, varname = "race", dist = "categorical", 
                         formula = genCatFormula(p1r,p2r,p3r))

def <- simstudy::defData(def, varname = "service", dist = "categorical", 
                         formula = genCatFormula(p1ser,p2ser,p3ser,p4ser))

def






 pop <- 10000
  
  p1a <- sample_df %>% filter(var %in% "age1") %>% pull(proportion)
  p2a <- sample_df %>% filter(var %in% "age2") %>% pull(proportion)
  p3a <- sample_df %>% filter(var %in% "age3") %>% pull(proportion)
  p4a <- sample_df %>% filter(var %in% "age4") %>% pull(proportion)
  p5a <- sample_df %>% filter(var %in% "age5") %>% pull(proportion)
  p6a <- sample_df %>% filter(var %in% "age6") %>% pull(proportion)
  
  p1s <- sample_df %>% filter(var %in% "sex1") %>% pull(proportion)
  p2s <- sample_df %>% filter(var %in% "sex2") %>% pull(proportion)
  
  p1g <- sample_df %>% filter(var %in% "grade1") %>% pull(proportion)
  p2g <- sample_df %>% filter(var %in% "grade2") %>% pull(proportion)
  p3g <- sample_df %>% filter(var %in% "grade3") %>% pull(proportion)
  p4g <- sample_df %>% filter(var %in% "grade4") %>% pull(proportion)
  
  p1r <- sample_df %>% filter(var %in% "race1") %>% pull(proportion)
  p2r <- sample_df %>% filter(var %in% "race2") %>% pull(proportion)
  p3r <- sample_df %>% filter(var %in% "race3") %>% pull(proportion)
  
  p1ser <- sample_df %>% filter(var %in% "service1") %>% pull(proportion)
  p2ser <- sample_df %>% filter(var %in% "service2") %>% pull(proportion)
  p3ser <- sample_df %>% filter(var %in% "service3") %>% pull(proportion)
  p4ser <- sample_df %>% filter(var %in% "service4") %>% pull(proportion)



genData(pop, def)

```







```{r}
set.seed(82)


sim_fun = function(df) {

 # pop <- df %>% filter(var %in% "service1") %>% pull(sum_pop) %>% round(., digits = 0)
  
  pop <- 10000
  
  p1a <- df %>% filter(var %in% "age1") %>% pull(proportion)
  p2a <- df %>% filter(var %in% "age2") %>% pull(proportion)
  p3a <- df %>% filter(var %in% "age3") %>% pull(proportion)
  p4a <- df %>% filter(var %in% "age4") %>% pull(proportion)
  p5a <- df %>% filter(var %in% "age5") %>% pull(proportion)
  p6a <- df %>% filter(var %in% "age6") %>% pull(proportion)
  
  p1s <- df %>% filter(var %in% "sex1") %>% pull(proportion)
  p2s <- df %>% filter(var %in% "sex2") %>% pull(proportion)
  
  p1g <- df %>% filter(var %in% "grade1") %>% pull(proportion)
  p2g <- df %>% filter(var %in% "grade2") %>% pull(proportion)
  p3g <- df %>% filter(var %in% "grade3") %>% pull(proportion)
  p4g <- df %>% filter(var %in% "grade4") %>% pull(proportion)
  
  p1r <- df %>% filter(var %in% "race1") %>% pull(proportion)
  p2r <- df %>% filter(var %in% "race2") %>% pull(proportion)
  p3r <- df %>% filter(var %in% "race3") %>% pull(proportion)
  
  p1ser <- df %>% filter(var %in% "service1") %>% pull(proportion)
  p2ser <- df %>% filter(var %in% "service2") %>% pull(proportion)
  p3ser <- df %>% filter(var %in% "service3") %>% pull(proportion)
  p4ser <- df %>% filter(var %in% "service4") %>% pull(proportion)

  


def <- simstudy::defData(varname = "age", dist = "categorical", 
                         formula = genCatFormula(p1a,p2a,p3a,p4a,p5a,p6a))

def <- simstudy::defData(def, varname = "sex", dist = "categorical", 
                         formula = genCatFormula(p1s,p2s))

def <- simstudy::defData(def, varname = "grade", dist = "categorical", 
                         formula = genCatFormula(p1g,p2g,p3g,p4g))

def <- simstudy::defData(def, varname = "race", dist = "categorical", 
                         formula = genCatFormula(p1r,p2r,p3r))

def <- simstudy::defData(def, varname = "service", dist = "categorical", 
                         formula = genCatFormula(p1ser,p2ser,p3ser,p4ser))

def

genData(pop, def)

  
}





```




```{r}
sim <-
  demog_long %>%
    nest(data = -year) %>% 
      mutate(sim = map(.x = data, .f = sim_fun)) 


sim$sim[4] %>% 
  as.data.frame() %>% 
  as_tibble()


warnings()


demog_long$proportion 

demog_long %>% 
  filter(cat %in% "grade") %>% View()
  group_by(year) %>%
  summarise(prop_sum = sum(proportion))



```







