---
title: "3a-attributal_risk"
author: "SL"
date: "6/01/2021"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(haven)
library(Hmisc)
library(janitor)
library(skimr)
library(zoo)
library(naniar)
library(broom)
library(MASS)
library(viridis)
library(ggrepel)

memory.limit(size = 50000)
# rm(list = ls())
```


```{r}

hsi_rf <- read_rds("data/hsi_rf.rds")

#hsi_rf %>% skimr::skim()
# hsi_rf %>% count(var)
```

Recode category names
Restrict to 1998 - 2019

```{r}

hsi_factors <-
  hsi_rf %>%
    dplyr::filter(year > 1997 & year < 2020) %>% 
     mutate(
          var = recode(
            var,
              "sex1" = "Male",
              "sex2" = "Female",
              "race1" = "White",
              "race2" = "Black",
              "race3" = "Other",
              "service1" = "Army",
              "service2" = "Navy",
              "service3" = "Air Force",
              "service4" = "Marine Corps",
              "age1" = "<20",
              "age2"= "20-24",
              "age3" = "25-29",
              "age4" = "30-34",
              "age5" = "35-39",
              "age6" = ">=40",
              "grade1" = "E1-E4",
              "grade2" = "E5-E9",
              "grade3" = "O1-O3/W1-W3" ,
              "grade4" = "O4-O10/W4-W5")
          )

hsi_factors

# write_rds(hsi_factors, "data/hsi_factors.rds")
```




## Risk over time

```{r}


hsi_factors %>%
   mutate(label = if_else(year == max(year), as.character(var), NA_character_),
          Risk = risk * 10000) %>%
   ggplot(aes(x = as.integer(year), y = Risk)) +
    geom_point(aes(shape = var)) +
    geom_line(aes(color = var)) +
    facet_grid(cat~.) +
    geom_text_repel(aes(label = label),
                  nudge_x = 1,
                  size = 3,
                  na.rm = TRUE) +
    theme_bw() +
    theme(legend.position = "none") +
    scale_shape_manual(values = rep(c(0:10, 12, 13, 15:20), 2)) +
    scale_x_continuous(breaks = scales::pretty_breaks(10)) + 
  labs(x = "Year",
       y = "HSI cases per 10,000")



# heatmap 

hsi_rf %>% 
  ggplot(aes(x = as.integer(year), y = var, fill = risk)) +
  geom_tile() +
  scale_fill_viridis(discrete = FALSE) +
  theme_bw()

```



## Risk factor proportion

```{r}

hsi_rf %>% 
  mutate(var_num = str_extract(var, "[:digit:]")) %>% 
  ggplot(aes(x = as.integer(year), y = prop_ratio, color = cat, shape = var_num)) +
    geom_point() +
    geom_line() +
  theme_bw()


# heatmap

hsi_rf %>% 
  ggplot(aes(x = as.integer(year), y = var, fill = prop_ratio)) +
  geom_tile() +
  scale_fill_viridis(discrete = FALSE) +
  theme_bw()


```




## Statistical Tests


Chi-square goodness of fit: Compare multiple observed proportions to expected probabilities


Null hypothesis (H0): There is no significant difference between the observed and the expected value.
Alternative hypothesis (Ha): There is a significant difference between the observed and the expected value.


simulate.p.value = TRUE, a logical indicating whether to compute p-values by Monte Carlo simulation.
fisher.test(a)

```{r}

chisq <-
  hsi_rf %>% 
    nest(data = c(-year, -cat)) %>% 
    mutate(chisq =
             map(data,
             ~chisq.test(x = .$n, p = .x$proportion))
  )




chisq_sim <-
  hsi_rf %>% 
    nest(data = c(-year, -cat)) %>% 
    mutate(chisq =
             map(data,
             ~chisq.test(x = .$n, p = .x$proportion,
                         simulate.p.value = TRUE, B = 2000))
  )


# write_rds(chisq_sim, file = "data/chisq_sim")

chisq_sim <- read_rds(file = "data/chisq_sim")


chisq_sim <-
  chisq_sim %>% 
    mutate(chisq_tidy = map(chisq, broom::tidy))


chisq_sim


# Chisq significance stars

chisq_sim %>% 
  unnest(chisq_tidy) %>%
  dplyr::select(year, cat, statistic, p.value) %>% 
   mutate(signif = case_when(
        p.value <= 0.05 & p.value > 0.01 ~ "*",
        p.value <= 0.01 & p.value > 0.001 ~ "**",
        p.value <= 0.001 ~ "***",
        TRUE ~ ""
    )) 

# Chisq significance, wide table by year
chisq_sig_wide <-
  chisq_sim %>% 
    dplyr::filter(year > 1997 & year < 2020) %>% 
    unnest(chisq_tidy) %>%
    dplyr::select(year, cat, statistic, p.value) %>% 
    mutate(signif = case_when(
        p.value <= 0.05 & p.value > 0.01 ~ "*",
        p.value <= 0.01 & p.value > 0.001 ~ "**",
        p.value <= 0.001 ~ "***",
        TRUE ~ ""
    )) %>%
    dplyr::select(year, cat, signif) %>% 
    pivot_wider(names_from = year, values_from = signif) 


chisq_sig_wide 

chisq_sig_wide %>% 
  clipr::write_clip()

# Chi sq Values table

chisq_val_wide <-
  chisq_sim %>% 
    dplyr::filter(year > 1997 & year < 2020) %>% 
    unnest(chisq_tidy) %>%
    dplyr::select(year, cat, statistic, p.value) %>% 
    mutate(signif = case_when(
        p.value <= 0.05 & p.value > 0.01 ~ "*",
        p.value <= 0.01 & p.value > 0.001 ~ "**",
        p.value <= 0.001 ~ "***",
        TRUE ~ ""
    )) %>%
    dplyr::select(year, cat, statistic) %>% 
    pivot_wider(names_from = year, values_from = statistic) 

chisq_val_wide 

chisq_val_wide %>% 
  clipr::write_clip()

```



