
---
title: "4_report"
author: "SL"
date: "5/17/2021"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(haven)
library(Hmisc)
library(janitor)
library(skimr)
library(zoo)
library(naniar)
library(scales)
library(viridis)
library(RColorBrewer)
library(ggrepel)
library(table1)
library(gmodels)

```



```{r}

df_hsi <- read_rds("data/df_hsi.rds")

Hmisc::describe(df_hsi)

hsi_factors <- read_rds("data/hsi_factors.rds")

#hsi_factors %>% count(var)
```


## Table 1


Recode for display
Restrict to years: 1998 - 2019

```{r}



df_hsi %>% count(service)


df_hsi_table_other <-
  df_hsi %>%
    dplyr::filter(year > 1997 & year < 2020) %>% 
     dplyr::select(source, age, sex, race_ethnic, service, grade, hsi, bmi, casedef, bmi_cat, year) %>% 
       mutate(service = recode_factor(service,
            "A" = "Army",
            "N" = "Navy",
            "F" = "Air Force",
            "M" = "Marine Corps",
            "C" = "Coast Guard"
            ),
            source = recode_factor(source,
            "INPATIENT" = "In-Patient",
            "OUTPATIENT" = "Out-Patient",
            "RME" = "Reportable Event"),
            hsi = recode_factor(hsi,
            "heat_stroke" = "Heat Stroke",
            "heat_exhaustion" = "Heat Exhaustion",
            "other" = "Other"),
            sex = recode_factor(sex,
            "M" = "Male",
            "F" = "Female",
            "Z" = "Unknown")
            ) %>% 
            haven::zap_label()




df_hsi_table <-
  df_hsi_table_other %>%
    dplyr::filter(!hsi %in% "Other") 

    
```


## Table formatting
```{r}


# formatting for comma separators, https://github.com/benjaminrich/table1/issues/34

render.continuous <- function(x, ...) {
    with(stats.default(x, ...), c("",
        "Mean (SD)"         = sprintf("%s (%s)",
          signif_pad(MEAN,   3, big.mark=","),
          signif_pad(SD,     3, big.mark=",")),
        "Median [Min, Max]" = sprintf("%s [%s, %s]",
          signif_pad(MEDIAN, 3, big.mark=","),
          signif_pad(MIN,    3, big.mark=","),
          signif_pad(MAX,    3, big.mark=","))))
}


render.categorical <- function(x, ...) {
    c("", sapply(stats.apply.rounding(stats.default(x)), function(y) with(y,
      sprintf("%s (%s%%)", prettyNum(FREQ, big.mark=","), PCT))))
}

render.strat <- function (label, n, ...) {
    sprintf("<span class='stratlabel'>%s<br><span class='stratn'>(N=%s)</span></span>", 
        label, prettyNum(n, big.mark=","))
}


```





## Outcome table including "other HSI"
```{r}

# by casedef (keep "1" and "overall" columns)
table1::table1(~ hsi + source + sex + age + sex + race_ethnic + grade + service + bmi + bmi_cat  | casedef, data = df_hsi_table_other)





# by casedef (keep "1" and "overall" columns)
table1::table1(~ hsi + source + sex + age + sex + race_ethnic + grade + service + bmi + bmi_cat  | casedef, data = df_hsi_table_other, render.continuous = render.continuous, render.categorical = render.categorical, render.strat = render.strat)


```

## Restrict to heat stroke and heat exhaustion

```{r}

table_1 <-
 table1::table1(~ hsi + source + sex + age + sex + race_ethnic + grade + service + bmi + bmi_cat  | casedef, data = df_hsi_table, , render.continuous = render.continuous, render.categorical = render.categorical, render.strat = render.strat)    

table_1
```



## Cross-Tabulation

```{r}

# Among Casedef

df_hsi_table %>%
  dplyr::filter(casedef == 1) %>% 
  dplyr::count(age, grade, sex, race_ethnic)

# age and grade

df_hsi_table %>%
  dplyr::filter(casedef == 1) %>% 
  dplyr::count(age, grade)


df_hsi_casedef <- 
  df_hsi_table %>%
  dplyr::filter(casedef == 1)

age_grade_crosstab <-
  gmodels::CrossTable(df_hsi_casedef$age, df_hsi_casedef$grade, prop.chisq = FALSE, chisq = TRUE)


gmodels::CrossTable(df_hsi_casedef$age, df_hsi_casedef$grade, 
                    prop.r = FALSE, prop.c = FALSE, prop.t = FALSE, prop.chisq = FALSE)


age_grade_crosstab 
# write_rds(age_grade_crosstab, file = "output/age_grade_crosstab.rds")



# race and service

df_hsi_table %>%
  dplyr::filter(casedef == 1) %>% 
  dplyr::count(service, race_ethnic)


gmodels::CrossTable(df_hsi_casedef$service, df_hsi_casedef$race_ethnic)

race_service_crosstab <-
  gmodels::CrossTable(df_hsi_casedef$service, df_hsi_casedef$race_ethnic, prop.chisq = FALSE, chisq = TRUE)

race_service_crosstab
# write_rds(race_service_crosstab, file = "output/race_service_crosstab.rds")




```





## BMI Table

Restrict to Age < 25
Case-definition applied


```{r}

df_hsi_table_bmi <-
  df_hsi_table %>% 
    dplyr::filter(age %in% c("<20", "20-24"),
                  casedef == 1)


table1::table1(~ bmi |  hsi, data = df_hsi_table_bmi)
table1::table1(~ bmi |  source, data = df_hsi_table_bmi)    
table1::table1(~ bmi |  sex, data = df_hsi_table_bmi)
table1::table1(~ bmi |  race_ethnic, data = df_hsi_table_bmi)
table1::table1(~ bmi |  grade, data = df_hsi_table_bmi)    
table1::table1(~ bmi |  as_factor(year), data = df_hsi_table_bmi)   

table1::table1(~ bmi |  hsi * source, data = df_hsi_table_bmi)  
table1::table1(~ bmi_cat |  hsi * source, data = df_hsi_table_bmi)  
```


Including "other" hsi

```{r}
df_hsi_table_bmi_other <-
  df_hsi_table_other %>% 
    dplyr::filter(age %in% c("<20", "20-24"),
                  casedef == 1)


table1::table1(~ bmi |  hsi, data = df_hsi_table_bmi_other)
table1::table1(~ bmi |  source, data = df_hsi_table_bmi_other)    

table1::table1(~ bmi |  hsi * source, data = df_hsi_table_bmi_other)  
table1::table1(~ bmi_cat |  hsi * source, data = df_hsi_table_bmi_other) 

```



## Figures


```{r}


df_hsi_table %>%
  dplyr::filter(casedef == 1) %>% count(service)

# Case definition

df_hsi_table %>%
  dplyr::filter(casedef == 1) %>% 
  group_by(year, hsi) %>%
  summarise(n = dplyr::n()) %>%
  ggplot(aes(x = year, y = n, color = hsi)) +
    geom_point(size = 1.2) +
    geom_line(size = 1) +
    geom_smooth(method = lm) +
  labs(x = "Year",
       y = "HSI cases",
       color = "Diagnosis") +
  theme_bw() +
  scale_x_continuous(breaks = scales::breaks_pretty(n = 9)) +
  theme(legend.position = "bottom") +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1))




# ggsave(filename = "output/case_def_line_plot.tiff")

df_hsi_table %>%
  dplyr::filter(casedef == 1) %>% 
  group_by(year, hsi) %>%
  summarise(n = dplyr::n()) %>%
  ggplot(aes(x = year, y = n, color = hsi)) +
    geom_point(size = 1.5) +
    geom_line(size = 1.5) +
    geom_smooth(method = lm) +
  labs(x = "Year",
       color = "Diagnosis") +
  theme_bw() +
  scale_x_continuous(breaks = scales::breaks_pretty(n = 9))





# Plot facet: Type/ source
df_hsi_table %>%
  dplyr::filter(casedef == 1) %>% 
  group_by(year, hsi, source) %>%
  summarise(n = dplyr::n()) %>%
  ggplot(aes(x = year, y = n, color = hsi)) +
    facet_wrap(~source) +
    geom_point(size = 1) +
    geom_line(size = 1) +
    geom_smooth(method = lm) +
  labs(x = "Year",
       y = "HSI cases",
       color = "Diagnosis") +
  theme_bw() +
  scale_x_continuous(breaks = scales::breaks_pretty(n = 6)) +
  theme(legend.position = "bottom") +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1))


# ggsave(filename = "output/hsi_type_source.tiff")



# Service and Sex, Coast Guard and Unknown sex filtered

df_hsi_table %>%
  dplyr::filter(casedef == 1,
                  !service %in% "Coast Guard",
                  !sex %in% "Unknown") %>% 
  group_by(year, service, sex) %>%
  summarise(n = dplyr::n()) %>%
  ggplot(aes(x = year, y = n, color = sex)) +
    facet_wrap(~service) +
    geom_point(size = 1) +
    geom_line(size = 1) +
    geom_smooth(method = lm) +
  labs(x = "Year",
       y = "HSI cases",
       color = "Sex") +
  theme_bw() +
  scale_x_continuous(breaks = scales::breaks_pretty(n = 6)) +
  theme(legend.position = "bottom") +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1))

# ggsave(filename = "output/hsi_service_sex.tiff")



# Race and Sex, Unknown sex filtered

df_hsi_table %>%
  dplyr::filter(casedef == 1,
                  !sex %in% "Unknown") %>% 
  group_by(year, race_ethnic, sex) %>%
  summarise(n = dplyr::n()) %>%
  ggplot(aes(x = year, y = n, color = race_ethnic)) +
    facet_wrap(~sex) +
    geom_point(size = 1) +
    geom_line(size = 1) +
    geom_smooth(method = lm) +
  labs(x = "Year",
       y = "HSI cases",
       color = "Race/Ethnicity") +
  theme_bw() +
  scale_x_continuous(breaks = scales::breaks_pretty(n = 6)) +
  theme(legend.position = "bottom") +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1))

# ggsave(filename = "output/hsi_race_sex.tiff")





# Service and race, Coast Guard filtered

df_hsi_table %>%
  dplyr::filter(casedef == 1,
                !service %in% "Coast Guard") %>% 
  group_by(year, service, race_ethnic) %>%
  summarise(n = dplyr::n()) %>%
  ggplot(aes(x = year, y = n, color = race_ethnic)) +
    facet_wrap(~service) +
    geom_point(size = 1) +
    geom_line(size = 1) +
    geom_smooth(method = lm) +
  labs(x = "Year",
       y = "HSI cases",
       color = "Race/Ethnicity") +
  theme_bw() +
  scale_x_continuous(breaks = scales::breaks_pretty(n = 6)) +
  theme(legend.position = "bottom") +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1))

# Age Groups and Sex
  # filter sex %in% 'Unknown' & age %in% NA

df_hsi_table %>%
  dplyr::filter(casedef == 1,
                !sex %in% "Unknown",
                !age %in% NA) %>% 
  group_by(year, sex, age) %>%
  summarise(n = dplyr::n()) %>%
  ggplot(aes(x = year, y = n, color = age)) +
    facet_wrap(~sex) +
    geom_point(size = 1) +
    geom_line(size = 1) +
    geom_smooth(method = lm) +
  labs(x = "Year",
       y = "HSI cases",
       color = "Age Group") +
  theme_bw() +
  scale_x_continuous(breaks = scales::breaks_pretty(n = 6)) +
  theme(legend.position = "bottom") +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1))




## Table
df_hsi_table %>%
  dplyr::filter(casedef == 1) %>% 
  group_by(year, hsi) %>%
  summarise(n = dplyr::n()) %>% 
  tidyr::pivot_wider(names_from = hsi, values_from = n) %>% 
  mutate(sum = (`Heat Stroke` + `Heat Exhaustion`)) %>% View()



# linear model 

lm_models <-
  df_hsi_table %>%
    dplyr::filter(casedef == 1) %>% 
    group_by(year, hsi) %>%
    summarise(n = dplyr::n()) %>%
    nest(data = -hsi) %>% 
    mutate(lm_mod =
             map(.$data, ~lm(n ~ year, data = .x))
    )


lm_models$lm_mod %>% map(., broom::tidy)
lm_models$lm_mod %>% map(., broom::glance)
    


df_hsi_table %>%
  dplyr::filter(casedef == 1) %>% 
  group_by(year, hsi, source) %>%
  summarise(n = dplyr::n()) %>%
  ggplot(aes(x = year, y = n, color = hsi)) +
    geom_point(size = 1.5) +
    geom_line(size = 1.5) +
    geom_smooth(method = lm) +
    facet_grid(source ~.) +
  labs(x = "Year",
       color = "Type") +
  theme_bw() 




# all encounters, with other

df_hsi_table_other %>%
  group_by(year, hsi) %>%
  summarise(n = dplyr::n()) %>%
  ggplot(aes(x = year, y = n, color = hsi)) +
    geom_point(size = 1.6) +
    geom_line(size = 1.5) +
    geom_smooth(method = lm, alpha = 0.2) +
  labs(x = "Year",
       color = "Type") +
  theme_bw() 


df_hsi_table_other %>%
  group_by(year, hsi, source) %>%
  summarise(n = dplyr::n()) %>%
  ggplot(aes(x = year, y = n, color = hsi)) +
    geom_point(size = 1.6) +
    geom_line(size = 1.5) +
    geom_smooth(method = lm, alpha = 0.2) +
  facet_grid(source ~.) +
  labs(x = "Year",
       color = "Type") +
  theme_bw() 

```



# Risk plot
```{r}
cbp1 <- c("#999999", "#E69F00", "#56B4E9", "#009E73",
          "#F0E442", "#0072B2", "#D55E00", "#CC79A7",
          "#999999", "#E69F00", "#56B4E9", "#009E73",
          "#F0E442", "#0072B2",  "#009E73", "#D55E00",
          "#999999", "#E69F00", "#56B4E9", "#009E73")




hsi_factors %>%
   mutate(label = if_else(year == max(year), as.character(var), NA_character_),
          Risk = risk * 10000) %>%
   ggplot(aes(x = as.integer(year), y = Risk)) +
    geom_line(aes(color = var), size = 1.5) +
    geom_point(aes(shape = var), size = 1.5) +
    facet_grid(cat~.) +
    geom_text_repel(aes(label = label),
                  nudge_x = 1,
                  size = 3,
                  na.rm = TRUE) +
    theme_bw() +
    theme(legend.position = "none") +
    scale_shape_manual(values = rep(c(0:10, 12, 13, 15:20), 2)) +
    scale_colour_manual(values = cbp1) +
    #scale_color_viridis(discrete = TRUE) +
    scale_x_continuous(breaks = scales::pretty_breaks(10)) +
    labs(x = "Year",
         y = "HSI cases per 10,000")

# ggsave("output/risk_plot.png")  


var_names <- as_labeller(
     c(`age` = "Age Group", `grade` = "Grade Group",`race` = "Race / Ethnicity", 
       `service` = "Service Branch",`sex` = "Sex"))



# 5 panel horizontal plot

hsi_factors %>%
   mutate(label = if_else(year == max(year), as.character(var), NA_character_),
          Risk = risk * 10000) %>%
   ggplot(aes(x = as.integer(year), y = Risk)) +
    geom_line(aes(color = var), size = 1.5) +
    geom_point(aes(shape = var), size = 1.5) +
    facet_grid(~cat, labeller = var_names) +
    geom_label_repel(aes(label = label),
                  nudge_x = 0,
                  size = 3,
                  fontface = "bold",
                  na.rm = TRUE) +
    theme_bw() +
    theme(legend.position = "none") +
    scale_shape_manual(values = rep(c(0:10, 12, 13, 15:20), 2)) +
    scale_colour_manual(values = cbp1) +
    #scale_color_viridis(discrete = TRUE) +
    scale_y_continuous(breaks = scales::pretty_breaks(8)) + 
    labs(x = "Year",
         y = "HSI cases per 10,000") +
    theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1))



# 2 x 3 wrap plot

hsi_factors %>%
   mutate(label = if_else(year == max(year), as.character(var), NA_character_),
          Risk = risk * 10000) %>%
   ggplot(aes(x = as.integer(year), y = Risk)) +
    geom_line(aes(color = var), size = 1.5) +
    geom_point(aes(shape = var), size = 1.5) +
    facet_wrap(~cat, labeller = var_names, nrow = 3) +
    geom_label_repel(aes(label = label),
                  nudge_x = 0,
                  size = 3,
                  fontface = "bold",
                  na.rm = TRUE) +
    theme_bw() +
    theme(legend.position = "none") +
    scale_shape_manual(values = rep(c(0:10, 12, 13, 15:20), 2)) +
    scale_colour_manual(values = cbp1) +
    #scale_color_viridis(discrete = TRUE) +
    scale_y_continuous(breaks = scales::pretty_breaks(8)) + 
    labs(x = "Year",
         y = "HSI cases per 10,000") +
    theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1))

# ggsave(filename = "output/risk_plot_2x3.tiff", device = "tiff", dpi = 500)

# ggsave("output/risk_plot_horiz.png")  
```

# Risk Table
```{r}

# Sum population

hsi_factors %>%
   mutate(label = if_else(year == max(year), as.character(var), NA_character_),
          Risk = risk * 10000) %>% 
   dplyr::filter(var %in% "<20") %>%  # filter by unique Variable to get one per year
   dplyr::select(year, sum_pop)
  


risk_table <-
  hsi_factors %>%
     mutate(label = if_else(year == max(year), as.character(var), NA_character_),
            Risk = risk * 10000) %>% 
    dplyr::select(year, var, cat, Risk) %>% 
    tidyr::pivot_wider(names_from = c(cat, var), values_from = Risk) 

risk_table

# write_csv(risk_table, file = "output/risk_table.csv")

```




# Observed / Expected

```{r}

hsi_factors %>%
   mutate(label = if_else(year == max(year), as.character(var), NA_character_),
          Risk = risk * 10000) %>%
   ggplot(aes(x = as.integer(year), y = prop_ratio)) +
    geom_line(aes(color = var), size = 1.5) +
    geom_point(aes(shape = var), size = 1.5) +
    geom_hline(yintercept = 1, linetype = "dashed") +
    facet_grid(~cat, labeller = var_names) +
    geom_label_repel(aes(label = label),
                  nudge_x = 0,
                  size = 3,
                  fontface = "bold",
                  na.rm = TRUE) +
    theme_bw() +
    theme(legend.position = "none") +
    scale_shape_manual(values = rep(c(0:10, 12, 13, 15:20), 2)) +
    scale_colour_manual(values = cbp1) +
    #scale_color_viridis(discrete = TRUE) +
    scale_y_continuous(breaks = scales::pretty_breaks(8)) + 
    labs(x = "Year",
         y = "Subgroup HSI Observed / Expected Ratio") +
    theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1)) 

# ggsave("output/risk_oe.png") 



hsi_factors %>%
   mutate(label = if_else(year == max(year), as.character(var), NA_character_),
          Risk = risk * 10000) %>%
   ggplot(aes(x = as.integer(year), y = prop_ratio)) +
    geom_line(aes(color = var), size = 1.5) +
    geom_point(aes(shape = var), size = 1.5) +
    geom_hline(yintercept = 1, linetype = "dashed") +
    facet_wrap(~cat, labeller = var_names, nrow = 3) +
    geom_label_repel(aes(label = label),
                  nudge_x = 0,
                  size = 3,
                  fontface = "bold",
                  na.rm = TRUE) +
    theme_bw() +
    theme(legend.position = "none") +
    scale_shape_manual(values = rep(c(0:10, 12, 13, 15:20), 2)) +
    scale_colour_manual(values = cbp1) +
    #scale_color_viridis(discrete = TRUE) +
    scale_y_continuous(breaks = scales::pretty_breaks(8)) + 
    labs(x = "Year",
         y = "Subgroup HSI Observed / Expected Ratio") +
    theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1)) 

# ggsave("output/risk_oe.png") 
# ggsave(filename = "output/oe_plot_2x3.tiff", device = "tiff", dpi = 500)




# O/E Table

oe_table <-
  hsi_factors %>%
     mutate(label = if_else(year == max(year), as.character(var), NA_character_),
            Risk = risk * 10000) %>% 
    dplyr::select(year, var, cat, prop_ratio) %>% 
    tidyr::pivot_wider(names_from = c(cat, var), values_from = prop_ratio) 


oe_table

# write_csv(oe_table, file = "output/oe_table.csv")



```


## BMI 

Restrict to Age < 25 for BMI analysis 


```{r}

df_bmi <-
    df_hsi %>%
    dplyr::filter(year > 1997 & year < 2020) %>% 
     dplyr::select(source, age, sex, race_ethnic, service, grade, hsi, bmi, casedef, bmi_cat, year, d_event) %>% 
       mutate(service = recode_factor(service,
            "A" = "Army",
            "N" = "Navy",
            "F" = "Air Force",
            "M" = "Marine Corps",
            "C" = "Coast Guard"
            ),
            source = recode_factor(source,
            "INPATIENT" = "In-Patient",
            "OUTPATIENT" = "Out-Patient",
            "RME" = "Reportable Event"),
            hsi = recode_factor(hsi,
            "heat_stroke" = "Heat Stroke",
            "heat_exhaustion" = "Heat Exhaustion",
            "other" = "Other"),
            sex = recode_factor(sex,
            "M" = "Male",
            "F" = "Female",
            "Z" = "Unknown")
            ) %>%
        dplyr::filter(!hsi %in% "Other",
                    age %in% c("<20", "20-24"),
                    casedef == 1) %>%  
        haven::zap_label()



df_bmi   

```




## BMI Tables

```{r}

# All

table1::table1(~ hsi + sex + age + sex + grade + race_ethnic + casedef  | bmi_cat, data = df_bmi, render.continuous = render.continuous, render.categorical = render.categorical, render.strat = render.strat)

table1::table1(~ bmi_cat + bmi | sex, data = df_bmi, render.continuous = render.continuous, render.categorical = render.categorical, render.strat = render.strat)


```


## BMI barplots
```{r}


# by year

df_bmi %>% 
  ggplot(aes(x = year, fill = bmi_cat)) +
    geom_bar(position = position_fill()) +
    theme_bw()

df_bmi %>%
  filter(!bmi_cat %in% NA) %>% 
  ggplot(aes(x = year, fill = bmi_cat)) +
    geom_bar(position = position_fill()) +
    theme_bw()


```


```{r}

# boxplot

df_bmi %>%
  ggplot(aes(x = as.factor(year), y = bmi)) +
    geom_boxplot() +
    theme_bw()


df_bmi %>%
  ggplot(aes(x = as.factor(year), y = bmi)) +
    geom_boxplot() +
    facet_wrap(~sex) +
    theme_bw()
```


```{r}

# scatterplot vy year

df_bmi %>% 
  ggplot(aes(x = year, y = bmi)) +
      geom_point() +
      geom_smooth(method = "lm") +
      theme_bw()


df_bmi %>% 
  ggplot(aes(x = year, y = bmi)) +
      geom_point(alpha = 0.1) +
      geom_smooth(method = "lm") +
     facet_wrap(~sex) +
      theme_bw() +
  scale_y_continuous(breaks = scales::pretty_breaks(8)) +
  labs(x = "Year",
       y = "BMI (kg/m²)") 

# ggsave("output/bmi_sex.png")

```


```{r}

# scatterplot by day

df_bmi %>% 
  ggplot(aes(x = d_event, y = bmi)) +
      geom_point() +
      geom_smooth(method = "lm") +
      theme_bw()


df_bmi %>% 
  ggplot(aes(x = d_event, y = bmi)) +
      geom_point(alpha = 0.2) +
      geom_smooth(method = "lm", fill = "cadetblue") +
     facet_wrap(~sex) +
      theme_bw() +
  scale_y_continuous(breaks = scales::pretty_breaks(8)) +
  labs(x = "Year",
       y = "BMI (kg/m²)") 

# ggsave(filename = "output/bmi_sex_day.tiff", device = "tiff", dpi = 500)
# ggsave("output/bmi_sex_day.png")



# BMI grid, sex/type
df_bmi %>% 
  ggplot(aes(x = d_event, y = bmi)) +
      geom_point(alpha = 0.2) +
      geom_smooth(method = "lm", fill = "cadetblue") +
     facet_grid(hsi ~ sex) +
      theme_bw() +
  scale_y_continuous(breaks = scales::pretty_breaks(8)) +
  labs(x = "Year",
       y = "BMI (kg/m²)") 

#ggsave(filename = "output/bmi_sex_day_type.tiff", device = "tiff", dpi = 500)


df_bmi %>% 
  ggplot(aes(x = d_event, y = bmi)) +
      geom_point(alpha = 0.2) +
      geom_smooth(method = "lm", size = 0.8, fill = "cadetblue") +
     facet_grid(hsi + source ~ sex) +
      theme_bw() +
  scale_y_continuous(breaks = scales::pretty_breaks(8)) +
  labs(x = "Year",
       y = "BMI (kg/m²)") 

# ggsave(filename = "output/bmi_sex_day_type_source.tiff", device = "tiff", dpi = 700, width = 5, height = 8, units = "in")

```





```{r}

# Linear model by year

df_bmi %>% 
  lm(bmi ~ year, data = .) %>% 
  broom::tidy()


df_bmi %>% 
  dplyr::filter(sex %in% "Male") %>% 
  lm(bmi ~ year, data = .) %>% 
  broom::tidy()


df_bmi %>% 
  dplyr::filter(sex %in% "Female") %>% 
  lm(bmi ~ year, data = .) %>% 
  broom::tidy()

```





```{r}

# Linear model by day

df_bmi %>% 
  lm(bmi ~ d_event, data = .) %>% 
  broom::tidy()


df_bmi %>% 
  dplyr::filter(sex %in% "Male") %>% 
  lm(bmi ~ d_event, data = .) %>% 
  broom::tidy()


df_bmi %>% 
  dplyr::filter(sex %in% "Female") %>% 
  lm(bmi ~ d_event, data = .) %>% 
  broom::tidy()

```








