---
title: "unused_code"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```




--------------------------------------------------------------------------
Draft code 

```{r}


  data.frame(
    age = sample(x= 1:6, size = 10000, replace = TRUE, prob = c(
      . %>% filter(var %in% "age1") %>% pull(proportion),
      . %>% filter(var %in% "age2") %>% pull(proportion),
      . %>% filter(var %in% "age3") %>% pull(proportion),
      . %>% filter(var %in% "age4") %>% pull(proportion),
      . %>% filter(var %in% "age5") %>% pull(proportion),
      . %>% filter(var %in% "age6") %>% pull(proportion)
      )),
    sex = sample(x = 1:2, size = 10000, replace = TRUE, prob = c(
      . %>% filter(var %in% "sex1") %>% pull(proportion),
      . %>% filter(var %in% "sex2") %>% pull(proportion)
       )),
    grade = sample(x = 1:4, size = 10000, replace = TRUE, prob = c(
      . %>% filter(var %in% "grade1") %>% pull(proportion),
      . %>% filter(var %in% "grade2") %>% pull(proportion),
      . %>% filter(var %in% "grade3") %>% pull(proportion),
      . %>% filter(var %in% "grade4") %>% pull(proportion)
    )),  
    race = sample(x = 1:3, size = 10000, replace = TRUE,prob = c(
      . %>% filter(var %in% "race1") %>% pull(proportion),
      . %>% filter(var %in% "race2") %>% pull(proportion),
      . %>% filter(var %in% "race3") %>% pull(proportion)
    )),  
    service = sample(x = 1:4, size = 10000, replace = TRUE, prob = c(
      . %>% filter(var %in% "service1") %>% pull(proportion),
      . %>% filter(var %in% "service2") %>% pull(proportion),
      . %>% filter(var %in% "service3") %>% pull(proportion),
      . %>% filter(var %in% "service4") %>% pull(proportion)
    ))
)



data_1990 <-
  demog_long %>%
    filter(year %in% "1990") %>% 
    dplyr::select(-year)





data.frame(
  age = sample(1:6, pop, replace = TRUE, prob = c(p1a, p2a, p3a, p4a, p5a, p6a)),
  sex = sample(1:2, pop, replace = TRUE, prob = c(p1s, p2s)),
  grade = sample(1:4, pop, replace = TRUE, prob = c(p1g, p2g, p3g, p4g)),  
  race = sample(1:3, pop, replace = TRUE, prob = c(p1r, p2r, p3r)),  
  service = sample(1:4, pop, replace = TRUE, prob = c(p1ser, p2ser, p3ser, p4ser))
)
  
  data_1990 %>% 
  

  
sample(c('male', 'female'), 10000, replace=TRUE)

 sample( LETTERS[1:4], 10000, replace=TRUE, prob=c(0.1, 0.2, 0.65, 0.05) ) %>% 
   as_tibble()
```


-----------------------------------------------------------

# Simulated demog df
# Logistic models




# Create numerically coded risk factor dataframe from `df_hsi` (cases) to match with `sim_df` (controls)

```{r}


# Note: race variable is crude, 7 categories in case dataframe, down to 3 in control dataframe (unknowns coded with "other")


df_hsi %>% 
  count(race_ethnic)


cases <-
  df_hsi %>% 
    filter(!service %in% "C",
           !year == 2020) %>%  # filter out Coast Guard encounters (not represented in controls)
    mutate(
      age = as.factor(case_when(
        age %in% "<20" ~ "1",
        age %in% "20-24" ~ "2",
        age %in% "25-29" ~ "3",
        age %in% "30-34" ~ "4",
        age %in% "35-39" ~ "5",
        age %in% ">=40" ~ "6"
               )),
      sex = as.factor(case_when(
        sex %in% "M" ~ "1",
        sex %in% "F" ~ "2"
               )),
      grade = as.factor(case_when(
        grade %in% "E1-E4" ~ "1",
        grade %in% "E5-E9" ~ "2",
        grade %in% "O1-O3/W1-W3" ~ "3",
        grade %in% "O4-O10/W4-W5" ~ "4"
               )),
      race_ethnic = as.factor(case_when(
        race_ethnic %in% "Non-Hispanic White" ~ "1",
        race_ethnic %in% "Non-Hispanic Black" ~ "2",
        race_ethnic %in% "American Indian/Alaskan Native" ~ "3",
        race_ethnic %in% "Asian/Pacific Islander" ~ "3",
        race_ethnic %in% "Hispanic" ~ "3",
        race_ethnic %in% "Other" ~ "3",
        race_ethnic %in% "Unknown" ~ "unknown"
               )),
      service = as.factor(case_when(
        service %in% "A" ~ "1",
        service %in% "N" ~ "2",
        service %in% "F" ~ "3",
        service %in% "M" ~ "4",
    ))) %>% 
  dplyr::select(year, age, sex, grade, race = race_ethnic, service, casedef) %>% 
  mutate(case = as.factor("1"),
         year = as.factor(year),
         race = na_if(race, "unknown"))


cases %>% 
  count(race)

cases %>% 
  Hmisc::describe()

```


Prepare control dataframe to match and join with case dataframe 
```{r}

controls <-
  sim_df %>% 
    dplyr::select(year, sim_pop) %>% 
    unnest(sim_pop) %>% 
    mutate(casedef = 0,
           case = 0) %>% 
    mutate_all(factor)

controls %>% 
  Hmisc::describe()

```



```{r}

case_control_df <-
  cases %>% 
    bind_rows(controls)

case_control_df %>% 
  Hmisc::describe()

# write_rds(case_control_df, file = "data/case_control_df.rds")

# case_control_df <- read_rds(file = "data/case_control_df.rds")  
```


Distribution of cases and their matched controls by risk factor levels

Overall (not nested by year)

```{r}

# Among case-definition cases...Slow!

#case_control_df %>% 
#  filter(!(casedef %in% "0" & case %in% "1")) %>% 
#  table1::table1(~ age + sex + grade + race + service | case, data = .)


# All 4-way combinations
case_control_df %>% 
  filter(casedef %in% "1") %>%
  dplyr::select(grade, sex, race, service) %>% 
  expand(grade, sex, race, service)


case_control_df %>% 
  filter(casedef %in% "1") %>%
  group_by(grade, sex, race, service) %>% 
  count() 
  

case_control_df %>%
  filter(casedef %in% "1") %>%
  count(race)
  
```


```{r}


casedef_df <-
  case_control_df %>% 
    filter(!(casedef %in% "0" & case %in% "1")) %>%  
    nest(data = -year) %>% 
    dplyr::arrange(year)
  


# write_rds(casedef_df, file = "data/casedef_df.rds")

# casedef_df <- read_rds(file = "data/casedef_df.rds")  


```

## Logistic regression models - all years (1990-2019)


```{r}
# Casedef
  

grade_glm_all_casedef <-
  case_control_df %>% 
      filter(!(casedef %in% "0" & case %in% "1"),
             as.integer(as.character(year)) > 1999) %>% 
      dplyr::select(year, grade, sex, race, service, case) %>%         
      filter(complete.cases(.)) %>%  
  glm(case ~ grade + sex + race + service,
           family = binomial, data = .)

write_rds(grade_glm_all_casedef, file = "data/grade_glm_all_casedef.rds")


broom::tidy(grade_glm_all_casedef) 
  



age_glm_all_casedef <-
  case_control_df %>% 
      filter(!(casedef %in% "0" & case %in% "1"),
             as.integer(as.character(year)) > 1999) %>% 
      dplyr::select(year, age, sex, race, service, case) %>%         
      filter(complete.cases(.)) %>%  
  glm(case ~ age + sex + race + service,
           family = binomial, data = .)

write_rds(age_glm_all_casedef, file = "data/age_glm_all_casedef.rds")


```






## Logistic regression models by year

```{r}

# Restrict years from: 2010 - 2019

casedef_df <-
  casedef_df %>% 
    dplyr::filter(as.integer(as.character(year)) > 2009) %>% 
     dplyr::filter(as.integer(as.character(year)) < 2020)

# logistic model for Grade, Sex, Race, Service


grade_glm = function(df) {
  glm(case ~ grade + sex + race + service,
           family = binomial, data = df)
}


# logistic model for Age, Sex, Race, Service

age_glm = function(df) {
  glm(case ~ age + sex + race + service,
           family = binomial, data = df)
}



casedef_nest <-
  casedef_df %>% 
  mutate(mod_grade = 
           map(data, grade_glm),
         mod_age = 
           map(data, age_glm))


#casedef_nest %>% 
 # dplyr::select(-data) %>% 
  # write_rds(., file = "data/casedef_mods.rds")

# casedef_nest <- read_rds(file = "data/casedef_mods.rds")  

casedef_nest$mod_grade[[1]]


# Model summaries

  # Glance
grade_glance <-
  map_df(casedef_nest$mod_grade, broom::glance) 

age_glance <-
  map_df(casedef_nest$mod_age, broom::glance) 

# write_rds(grade_glance, file = "data/grade_glance.rds")
# write_rds(age_glance, file = "data/age_glance.rds")

  # Tidy



grade_tidy <-
  map(.x = casedef_nest$mod_grade, broom::tidy) 
  

names(grade_tidy) <- casedef_nest$year

grade_tidy <-
  grade_tidy %>% 
    bind_rows(.id = "year")

grade_tidy

# write_rds(grade_tidy, file = "data/grade_tidy.rds")


age_tidy <-
  map(casedef_nest$mod_age, broom::tidy)


names(age_tidy) <- casedef_nest$year

age_tidy <-
  age_tidy %>% 
    bind_rows(.id = "year")


#write_rds(age_tidy, file = "data/age_tidy.rds")


# grade_tidy <- read_rds(file = "data/grade_tidy.rds")  
# age_tidy <- read_rds(file = "data/age_tidy.rds")  

```


```{r}

grade_confint <-
   map(.x = casedef_nest$mod_grade, MASS::Confint) 


class(casedef_nest$mod_grade[[1]])

confint(casedef_nest$mod_grade[[1]])
warnings()

```












---------------------------------------------------------
## Simstudy code
`simstudy` package

categorical
A categorical distribution is a discrete data distribution taking on values from 1 to K, with each value representing a specific category, and there are K categories. The categories may or may not be ordered. For a categorical variable with k categories, the formula is a string of probabilities that sum to 1, each separated by a semi-colon: (p1;p2;...;pk). p1 is the probability of the random variable falling in category 1, p2 is the probability of category 2, etc. The probabilities can be specified as functions of other variables previously defined. The link options are identity or logit. The variance field does not apply to the categorical distribution.

```{r}

set.seed(82)



def <- simstudy::defData(varname = "age", dist = "categorical", 
                         formula = "p1a;p2a;p3a;p4a;p5a;p6a")

def <- simstudy::defData(def, varname = "sex", dist = "categorical", 
                         formula = "p1s;p2s")

def <- simstudy::defData(def, varname = "grade", dist = "categorical", 
                         formula = "p1g;p2g;p3g;p4g")

def <- simstudy::defData(def, varname = "race", dist = "categorical", 
                         formula = "p1r;p2r;p3r")

def <- simstudy::defData(def, varname = "service", dist = "categorical", 
                         formula = "p1ser;p2ser;p3ser;p4ser")

def




sample_df <-
  demog_long %>% filter(year %in% "2019")



def <- simstudy::defData(varname = "age", dist = "categorical", 
                         formula = genCatFormula(p1a,p2a,p3a,p4a,p5a,p6a))

def <- simstudy::defData(def, varname = "sex", dist = "categorical", 
                         formula = genCatFormula(p1s,p2s))

def <- simstudy::defData(def, varname = "grade", dist = "categorical", 
                         formula = genCatFormula(p1g,p2g,p3g,p4g))

def <- simstudy::defData(def, varname = "race", dist = "categorical", 
                         formula = genCatFormula(p1r,p2r,p3r))

def <- simstudy::defData(def, varname = "service", dist = "categorical", 
                         formula = genCatFormula(p1ser,p2ser,p3ser,p4ser))

def






 pop <- 10000
  
  p1a <- sample_df %>% filter(var %in% "age1") %>% pull(proportion)
  p2a <- sample_df %>% filter(var %in% "age2") %>% pull(proportion)
  p3a <- sample_df %>% filter(var %in% "age3") %>% pull(proportion)
  p4a <- sample_df %>% filter(var %in% "age4") %>% pull(proportion)
  p5a <- sample_df %>% filter(var %in% "age5") %>% pull(proportion)
  p6a <- sample_df %>% filter(var %in% "age6") %>% pull(proportion)
  
  p1s <- sample_df %>% filter(var %in% "sex1") %>% pull(proportion)
  p2s <- sample_df %>% filter(var %in% "sex2") %>% pull(proportion)
  
  p1g <- sample_df %>% filter(var %in% "grade1") %>% pull(proportion)
  p2g <- sample_df %>% filter(var %in% "grade2") %>% pull(proportion)
  p3g <- sample_df %>% filter(var %in% "grade3") %>% pull(proportion)
  p4g <- sample_df %>% filter(var %in% "grade4") %>% pull(proportion)
  
  p1r <- sample_df %>% filter(var %in% "race1") %>% pull(proportion)
  p2r <- sample_df %>% filter(var %in% "race2") %>% pull(proportion)
  p3r <- sample_df %>% filter(var %in% "race3") %>% pull(proportion)
  
  p1ser <- sample_df %>% filter(var %in% "service1") %>% pull(proportion)
  p2ser <- sample_df %>% filter(var %in% "service2") %>% pull(proportion)
  p3ser <- sample_df %>% filter(var %in% "service3") %>% pull(proportion)
  p4ser <- sample_df %>% filter(var %in% "service4") %>% pull(proportion)



genData(pop, def)

```







```{r}
set.seed(82)


sim_fun = function(df) {

 # pop <- df %>% filter(var %in% "service1") %>% pull(sum_pop) %>% round(., digits = 0)
  
  pop <- 10000
  
  p1a <- df %>% filter(var %in% "age1") %>% pull(proportion)
  p2a <- df %>% filter(var %in% "age2") %>% pull(proportion)
  p3a <- df %>% filter(var %in% "age3") %>% pull(proportion)
  p4a <- df %>% filter(var %in% "age4") %>% pull(proportion)
  p5a <- df %>% filter(var %in% "age5") %>% pull(proportion)
  p6a <- df %>% filter(var %in% "age6") %>% pull(proportion)
  
  p1s <- df %>% filter(var %in% "sex1") %>% pull(proportion)
  p2s <- df %>% filter(var %in% "sex2") %>% pull(proportion)
  
  p1g <- df %>% filter(var %in% "grade1") %>% pull(proportion)
  p2g <- df %>% filter(var %in% "grade2") %>% pull(proportion)
  p3g <- df %>% filter(var %in% "grade3") %>% pull(proportion)
  p4g <- df %>% filter(var %in% "grade4") %>% pull(proportion)
  
  p1r <- df %>% filter(var %in% "race1") %>% pull(proportion)
  p2r <- df %>% filter(var %in% "race2") %>% pull(proportion)
  p3r <- df %>% filter(var %in% "race3") %>% pull(proportion)
  
  p1ser <- df %>% filter(var %in% "service1") %>% pull(proportion)
  p2ser <- df %>% filter(var %in% "service2") %>% pull(proportion)
  p3ser <- df %>% filter(var %in% "service3") %>% pull(proportion)
  p4ser <- df %>% filter(var %in% "service4") %>% pull(proportion)

  


def <- simstudy::defData(varname = "age", dist = "categorical", 
                         formula = genCatFormula(p1a,p2a,p3a,p4a,p5a,p6a))

def <- simstudy::defData(def, varname = "sex", dist = "categorical", 
                         formula = genCatFormula(p1s,p2s))

def <- simstudy::defData(def, varname = "grade", dist = "categorical", 
                         formula = genCatFormula(p1g,p2g,p3g,p4g))

def <- simstudy::defData(def, varname = "race", dist = "categorical", 
                         formula = genCatFormula(p1r,p2r,p3r))

def <- simstudy::defData(def, varname = "service", dist = "categorical", 
                         formula = genCatFormula(p1ser,p2ser,p3ser,p4ser))

def

genData(pop, def)

  
}





```




```{r}
sim <-
  demog_long %>%
    nest(data = -year) %>% 
      mutate(sim = map(.x = data, .f = sim_fun)) 


sim$sim[4] %>% 
  as.data.frame() %>% 
  as_tibble()


warnings()


demog_long$proportion 

demog_long %>% 
  filter(cat %in% "grade") %>% View()
  group_by(year) %>%
  summarise(prop_sum = sum(proportion))



```







